Titeln på avhandlingens språk

### 2022-11-02 background.tex
massaging sampling section
writing intro
working
discussing neuroticism

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{}
\end{figure}

@@

    \item The above effects are modulated by the Big Five~\cite{oliver:bfi1999} trait of \emph{neuroticism}, as evidenced by a \ac{PCA}.
\end{enumerate}

@@

>>>>

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \acl{WCA}}
\end{figure}

@@

    \item The above effects are modulated by the \acs*{BFI}~\cite{oliver:bfi1999} trait of \emph{neuroticism}.
    This is discussed in more detail below in \cref{ssec:moderationeffects}

    % , as evidenced by a \ac{PCA}.
\end{enumerate}

\subsubsection{Moderation of effects by individual characteristics}\label{ssec:moderationeffects}

As mentioned above, we collected variables related to well-known individual differences.
These encompassed both the \acf{BFI}, introduced by \textcite{oliver:bfi1999}, and the \acf{ITQ}, described by \textcite{witmer1998measuring}.
Out of the collected individual-difference variables, the most salient one corresponded to \emph{neuroticism}, a \ac{BFI} trait linked to low tolerance for stress and high emotional reactivity, and which has previously been linked to higher \emph{delay discounting} rates~\cite{hirsh2008delay}.
Delay discounting is the tendency to devalue rewards for which one must wait; high rates, indicative of waiting intolerance, have been associated with negative social and academic outcomes.

\begin{figure}
    \centering
    \includegraphics[width=.9\columnwidth]{figs/new_model/correlation_neuro_exectime.png}
    \caption{%
        Correlation between neuroticism and the mean execution time of the last four steps in blocks of \num{12} steps subject to the same \ac{TTF} in ~\textcite{olguinmunoz:impact2021}.
    }\label{fig:neuroexectimecorrel}
\end{figure}

Neuroticism was identified as a modulating factor for the previously discussed pacing effects through a \ac{PCA}.
Out of the three identified components, which cumulatively accounted for \SI{73.13}{\percent} of the variance in the results, neuroticism was included in the first two.
The effect of neuroticism was transversal to all \acp{TTF} and impairment durations in the tasks, and we show an example of this correlation between execution time and neuroticism in \cref{fig:neuroexectimecorrel}

Furthermore, we found that execution times were well-fit by an \ac{exGaussian} distribution, a distribution with ample body of research supporting its suitability for the modeling of the timing of human actions and reaction times~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
Fits were performed using the \ac{MLE} method.

@@

\todo[inline]{Include section on neuroticism? Ask Bobby?}

### 2022-11-02 model.tex
discussing neuroticism

The distribution chosen for the second variant described above corresponds to the \ac{exGaussian} distribution.
We've chosen this distribution due to the vast body of research supporting its suitability for the modeling of the timing of human actions~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
Fitting is done using \ac{MLE}.

>>>>

The distribution chosen for the second variant described above corresponds to the \ac{exGaussian} distribution, previously discussed in \cref{ssec:moderationeffects}.
Fitting is done using \ac{MLE}.
